\begin{thebibliography}{99}
%\addcontentsline{toc}{chapter}{参考文献}

\bibitem{google}
Google Inc. 「Google Maps」\\
https://www.google.com/maps

\bibitem{yahoo}
ヤフー株式会社 「Yahoo!カーナビ」\\
https://carnavi.yahoo.co.jp/

\bibitem{survey}
L. Mainetti, L. Patrono, I. Sergui,\\
``A Survey on Indoor positioning System'',\\
Int. Conf. on SoftCOM, pp. 111-120, Sep. 2014.

\bibitem{wifi}
Chouchang Yang and Huai-Rong Shao,\\
``WiFi-Based Indoor Positioning''\\
IEEE Communications Magazine, vol. 53, pp. 150-157, Mar. 2015.

\bibitem{optical}
Shenlong Wang, Sanja Fidler and Raquel Urtasun,\\
``Lost Shopping! Monocular Localization in Large indoor Spaces''\\
Int. Conf. on Computer Vision (ICCV), pp. 2695-2703, Dec. 2015.

\bibitem{imu}
Luan Van Nguyen and Hung Manh La,\\
``Real-Time Human Foot Motion Localization Algorithm With Dynamic Speed,'' \\
IEEE Trans. on Human-Machine Systems, vol. 46, no. 6, pp. 822-833, Dec. 2016.

\bibitem{indoorlocky}
梶 克彦，河口 信夫， \\
``indoor.Locky: UGCを利用した無線LAN屋内位置情報基盤''， \\
情報処理学会論文誌, vol. 52, no. 12, pp. 3263-3273, Dec. 2011.

\bibitem{indoorlocky2}
鈴木 友基，梶 克彦，河口 信夫， \\
``クラウドソーシングによる屋内構造地図情報の構築と収集''，\\
電子情報通信学会信学技報, Nov. 2011.

\bibitem{taiwa}
新田 知之，宮崎 和哉，吉見 駿，田端 亮介，新井 イスマイル，安積 卓也，西尾 信彦，\\
“視認性確認対話ベースの地下街ナビゲーションシステム”，\\
情報処理学会 インタラクション 2013

\bibitem{taiwa2}
Phan Duy Phuoc，宮島 智大，枇榔 晃裕，安積 卓也，西尾 信彦，\\
``広場通過を考慮した屋内ナビゲーションの手法検討''\\
電子情報通信学会技術研究報告, vol.2013-UBI-38, no. 56, pp. 313-318.

\bibitem{smartslam}
Hyojeong Shin, Yohan Chou, and Hojung Cha, \\
``Unsupervised Construction of an Indoor Floor Plan Using a Smartphone'',\\
IEEE Trans. on SMC Part C, vol. 42, no. 6, pp. 889-898, Nov. 2012.

\bibitem{crowdsourcing}
Jarhyun Yoo, H. Jim Kim, and Karl H. Johansson,\\
``Mapless Indoor Localization by Trajectory Learning from a Crowd'',\\
in Proc., Int. Conf. on IPIN, 2016.

\bibitem{meanshift}
D. Comaniciu and P. Meer, \\
``Mean shift: A robust approach toward feature space analysis'', \\
IEEE Trans. on PAMI, vol. 24, no. 5, pp. 603-619, 2002.

\bibitem{canny}
J. Canny, \\
``A Computational Approach To Edge Detection'', \\
IEEE Trans. on PAMI, vol. 8, no. 6, pp. 679-714, 1986.

\bibitem{swt}
B. Epshten, E. Ofek and Y. Wexler,\\
``Detecting Text in natural Scenes with Stroke Width Transform,'' \\
Int. Conf. on CVPR, pp. 13-18, Jun. 2010.

\bibitem{thinning}
Pratt, William K.,\\
``Digital Image Processing'',\\
John Wiley \& Sons, Inc., 1991.

\bibitem{smartpdr}
Wonho Kang and Youngnam Han, \\
``SmartPDR: Smartphone-Based Pedestrian Dead Reckoning for indoor Localization'', \\
IEEE Sensors Journal, vol. 15, no. 5, May 2015.

\bibitem{examplemapmatching1}
F. Zampella, A. R. J. Ruiz, and F. S. Granja, \\
``Indoor Positioning Using Efficient Map Matching, RSS Measurements, and an Improved Motion Model,'' \\
IEEE Trans. on Vehicular Technology, vol. 64, no. 4, pp. 1304-1317, Apr. 2015.

\bibitem{examplemapmatching2}
C. Ascher, A. Kesseler, M. Wankerl, and G. F. Trommer, \\
``Dual IMU Indoor Navigation with Particle Filter based Map-Matching on a Smartphone,''\\
in Proc., Int. Conf. on IPIN, 2010.

\bibitem{examplemapmatching3}
O. Woodman and R. Harle,\\
``Pedestrian Localisation for Indoor Environments,''\\
in Proc., 10th Int. Conf. UbiComp, pp. 114–123, 2008.

\bibitem{removereflect}
Yu Li, Michael S. Brown, \\
“Exploiting Reﬂection Change for Automatic Reﬂection Removal”,\\
Int. Conf. on Computer Vision, pp. 2432-2439, 2013.

\end{thebibliography}

%